---
title: "R Notebook"
output: html_notebook
---
## Load Data

```{r}
library(MASS)
library(tidyr)
library(ggplot2)
library(magrittr)
library(QTLRel)
```

## Part b

### House Age

House age does not seem to have a strong effect on median value. There is a baseline value around $25,000 that is consistent across house age.

```{r}
plot(Boston$age,Boston$medv)
```

### Number of Rooms
The number of rooms had a strong effect on median house value. Median value seems to have a linear dependence on number of rooms.

```{r}
plot(Boston$rm,Boston$medv)
```
### Effect of crime

Crime does seem to effect crime but there is a lack of resolution in the crime rate data.

```{r}
plot(Boston$crim,Boston$medv,log='x')
```
 
```{r}
plot(Boston$dis,Boston$medv)
```
### Lower Status of Population

Lower status has a strong effect on the 

```{r}
plot(Boston$lstat,Boston$medv)
```
 
```{r}
y_value = 'medv'
Boston %>%
  gather(-y_value, key = "var", value = "value") %>%
  ggplot(aes_string(x = "value", y = y_value)) +
    geom_point() +
    facet_wrap(~ var, scales = "free")+
    theme_bw()
```
 
## Part c

Distance, median value, bound by Charles River, and nox seem to have predictive relatinships with crime.

```{r}
summary(Boston$crim)
```

```{r}
y_value = 'crim'
Boston %>%
  gather(-y_value, key = "var", value = "value") %>%
  ggplot(aes_string(x = "value", y = y_value)) +
    geom_point() +
    facet_wrap(~ var, scales = "free")+
    theme_bw()
```


```{r}
plot(Boston$dis,Boston$crim,log='x')
```

## Part d

### Crime rate
```{r}
summary(Boston$crim)
```

The max crime rate is 89 which is an incredible 35,600% of the median value of .26.

```{r}
summary(Boston$tax)
```

The max tax rate is 711 which is 215% of the median value of 330.

```{r}
summary(Boston$ptratio)
```

The minimum, maximum, and media of pupil to teacher ratio is 12.60, 22.00, and 19.05.

## Part e

The number of 1 entries in chas column gives the number of towns bordering the river.

```{r}
length(Boston[Boston$chas==1,])
```

## Part f

```{r}
median(Boston$ptratio)
```

## Part g


```{r}
minTowns = c(which(Boston$medv==min(Boston$medv)))
Boston[minTowns,'medv',drop=FALSE]
```

```{r}
compareChart = data.frame(matrix(ncol=5,nrow=length(colnames(Boston))))
rownames(compareChart) <- colnames(Boston)
for (name in rownames(compareChart)){
  compareChart[name,]=c(Boston[minTowns,name],min(Boston[,name]),median(Boston[,name]),max(Boston[,name]))
}
colnames(compareChart) <- c(minTowns,'Min','Median','Max')
compareChart
```

## Part h


```{r}
sum(Boston$rm>7,na.rm=TRUE)
sum(Boston$rm>8,na.rm=TRUE)
```

